Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-05 Final-Draft.Rmd
Update Final-Draft.Rmd
changes

```{r, message=FALSE, include=FALSE}
#Longitudinal Model
set.seed(454)
pred_4 <- posterior_predict(
  complexmod,
  newdata = model_data, transform = TRUE)

@@

>>>>

```{r message=FALSE, include=FALSE}
#Longitudinal Model
set.seed(454)
pred_4 <- posterior_predict(
  complexmod,
  newdata = model_data, transform = TRUE)

@@

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) #Doesn't recognize state
set.seed(454)
pred_FL_RM <- posterior_predict(
  RM_model,
  newdata = new_FL)

pred_FL_RM <- data.frame(y_new = pred_FL[-1])

ggplot(pred_FL_RM, aes(x=y_new))+geom_density()

summary(pred_FL_RM)
```

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple") 
set.seed(454)
pred_FL_NR <- posterior_predict(
  NR_model,
  newdata = new_FL)

pred_FL_NR <- data.frame(y_new = pred_FL[-1])

ggplot(pred_FL_NR, aes(x=y_new))+geom_density()

summary(pred_FL_NR)
```

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
set.seed(454)
pred_FL_3 <- posterior_predict(
  model_3,
  newdata = new_FL)

pred_FL_3 <- data.frame(y_new = pred_FL[-1])

ggplot(pred_FL_3, aes(x=y_new))+geom_density()

summary(pred_FL_3)
```

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
set.seed(454)
pred_FL_complex <- posterior_predict(
  complexmod,
  newdata = new_FL)

pred_FL_complex <- data.frame(y_new = pred_FL[-1])

ggplot(pred_FL_complex, aes(x=y_new))+geom_density()

summary(pred_FL_complex)
```

```{r}

actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))

actual_FL_pred
```
